Fisher's method tables and plots

### 2019-01-16 Fishers_method/Fishers method tables and plots.Rmd

Table: RPE- Power of Fisher's method given large sample sizes for varying $\delta$ and true # of non-null effects (i.e. "Best-case scenario")
```{r, echo=FALSE, warning= FALSE, message = FALSE}
library(knitr)
library(tidyverse)
RPP_RPE_power_results <- readRDS("RPP_RPE_power_results.RDS")
table <- spread(RPP_RPE_power_results, key = delta, value = power)
table_rpp <- table[table$study == "RPP", -c(1,3, 4)]
table_rpe <- table[table$study == "RPE", -c(1,3, 4)]
kable(table_rpe, format="markdown", digits=4, align=c('l','r','r','r'),row.names = FALSE, col.names=c("# of false negatives","$\\delta=0.2$","$\\delta=0.5$","$\\delta=0.8$"),caption="RPE: Power to reject H0 with large n")
```

>>>>

Table: RPE- Power of Fisher's method given large sample sizes for varying $\delta$ and true # of non-null effects (i.e. "Best-case scenario")
```{r, echo=FALSE, warning= FALSE, message = FALSE}
library(knitr)
library(tidyverse)
RPP_RPE_power_results <- readRDS("./RPP_RPE_power_results.RDS")
table <- spread(RPP_RPE_power_results, key = delta, value = power)
table_rpp <- table[table$study == "RPP", -c(1,3, 4)]
table_rpe <- table[table$study == "RPE", -c(1,3, 4)]
kable(table_rpe, format="markdown", digits=4, align=c('l','r','r','r'),row.names = FALSE, col.names=c("# of false negatives","$\\delta=0.2$","$\\delta=0.5$","$\\delta=0.8$"),caption="RPE: Power to reject H0 with large n")
```
